A Switching Planner for Combined Task and Observation Planning

### 2010-11-25 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
I have to really rewrite the Switching section. Am doing that tonight and tomorrow.
 - Charles

We now describe our continual planning approach that switches between
sequential and decision-theoretic planning sessions.

Sequential planning proceeds in a continual manner until the
verification of an assumption about runtime state is scheduled. At
that point the system switches to a decision-theoretic planner that is
used to tailor sensory processing by the robot to test the validity of
the assumptions made so far.

>>>>

We describe our continual planning approach that switches between
sequential and decision-theoretic sessions. Continual planning and
execution proceeds in a POMDP described in DTPDDL. During sequential
sessions, planning is performed by a ``classical'' system,\footnote{By
``classical'', we mean a system the is designed to solve fully
observable deterministic tasks.}  and execution proceeds according to
the {\em trace} computed by that system. In the format of a classical
plan, that {\em trace} specifies a sequence of POMDP actions that
achieves the agent's objectives for a deterministic approximation,
i.e., {\em determinisation}, of the problem at hand. More precisely,
the trace is an interleaved sequence of POMDP actions and {\em
assumptive} actions. The latter give some of the assumptions the
planner makes about the truth value of {\em runtime state variables}
-- e.g. that a box of cornflakes is located in the kitchen at the
third plan step. Another kind of assumption, called an {\em
executability} assumption, is made when the trace includes an action
$\action$ that is not applicable with probability $1$ at the
belief-state
\bstate\ that the system is projected to be in when \action\ is executed, 
i.e., $\exists\state\in\states
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

A sequential session always proceeds first. Planning and execution are
interleaved according to the continual paradigm until an executability
assumption about an action, $\action$, scheduled for execution,
occurs. At this point our approach switches to using a
decision-theoretic solver which tailors sensory processing by the
agent to test the validity of the assumptions made in the trace,
including the truth value of $\poss(\action)$.

%% Sequential planning proceeds in a continual manner until the
%% verification of an assumption about runtime state is scheduled. At
%% that point the system switches to a decision-theoretic planner that is
%% used to tailor sensory processing by the robot to test the validity of
%% the assumptions made so far.
